---
title: "Voter Turnout Report"
output: html_document
---

```{r setup, include=FALSE}
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

# Load libraries
library(knitr)
library(tidyr)
library(ggplot2)
library(GGally)

# In this "setup" chunk, `source()` the `data-prep.R` file 
# The `all_data` object should now be available
source("data-prep.R")
```

## Voter Turnout
This is a brief report on voter turnout in each Washington State county in 2017. 

### Data Structure
Before exploring the data, it's important to understand how it's structured. For example:

The data has

- `r nrow(all_data)` rows
- `r ncol(all_data)` columns

Below is a table of descriptive statistics about each column.

```{r}
# Compute and format the summary statistics -- thanks, SO
# https://stackoverflow.com/questions/30520350/convert-summary-to-data-frame
formatted <- do.call(cbind, lapply(all_data, summary))

# Pass the formatted summary statistics to the `kable()` function
kable(formatted)
```

### Univariate analysis: how is each variable distributed?
Below is a histogram of each variable.

```{r}
# Use tidyr to gather the columns into two colums: feature and value
# Then use ggplot's `facet()` method to create small multiples
long_data <- all_data %>% 
  gather(key = "feature", value = "value", -county)

# Create a histogram
ggplot(long_data) +
  geom_histogram(mapping = aes(x = value)) +
  facet_wrap(~feature)
```

Unfortunately, the different orders of magnitude preclude meaningful information from being expressed in a number of columns. Below are the violin plots for percentage of males/females in each county.

```{r}
# Select just the "percentage" columns
perc_data <- long_data %>% 
  filter(grepl("perc", feature)) 

# Create a violin plot
ggplot(perc_data) +
  geom_violin(mapping = aes(x = feature, y = value)) 
```

The obvious question is, which counties have the highest percentage of voters?

```{r}
# Graph the percentage of voters in each county:
# To do this, the data frame needs to be sorted -- thanks, SO
# https://stackoverflow.com/questions/5208679/order-bars-in-ggplot2-bar-graph
all_data <- all_data %>% 
  mutate(total_percentage = total.voted / total.population) %>% 
  arrange(total_percentage)

ggplot(all_data) +
  geom_col(mapping = aes(x = county, y = total_percentage)) +
  scale_x_discrete(limits = all_data$county) +
  coord_flip()
```

### Multivariate analysis: which variables are co-related?
Below is a scatterplot matrix of the quantitative variables.

```{r}
ggpairs(all_data %>% select(-county))
```
