---
title: "Voter Turnout Report"
output: html_document
---

```{r setup, include=FALSE}
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

# Load libraries
library(knitr)
library(tidyr)
library(ggplot2)
library(GGally)

# In this "setup" chunk, `source()` the `data-prep.R` file 
# The `all_data` object should now be available
```

## Voter Turnout
This is a brief report on voter turnout in each Washington State county in 2017. 

### Data Structure
Before exploring the data, it's important to understand how it's structured. For example:

The data has

- N rows
- N columns

Below is a table of descriptive statistics about each column.

```{r}
# Compute and format the summary statistics -- thanks, SO
# https://stackoverflow.com/questions/30520350/convert-summary-to-data-frame

# Pass the formatted summary statistics to the `kable()` function
```

### Univariate analysis: how is each variable distributed?
Below is a histogram of each variable.

```{r}
# Use tidyr to gather the columns into two columns: feature and value
# Then use ggplot's `facet()` method to create small multiples

# Create a set of histogram
```

Unfortunately, the different orders of magnitude preclude meaningful information from being expressed in a number of columns. Below are the violin plots for percentage of males/females in each county.

```{r}
# Select just the rows with "percentages" from the long dataset you created

# Create a violin plot showing the percentages
```

The obvious question is, which counties have the highest percentage of voters?

```{r}
# Graph the percentage of voters in each county:
# To do this, the data frame needs to be sorted -- thanks, SO
# https://stackoverflow.com/questions/5208679/order-bars-in-ggplot2-bar-graph



```

### Multivariate analysis: which variables are co-related?
Below is a scatterplot matrix of the quantitative variables.

```{r}
# Use `ggpairs` to create a scatterplot matrix
```
